### 2019-03-16 README.Rmd
Misc cleanup

The back-end database, [MonetDB](https://monetdb.org) is very fast and powerful, making such
analyses quite snappy even on such large data using normal desktops and laptops. Here's the
timing of the above query, which processes over 20 million records, on an ordinary laptop:

>>>>

The back-end database, [MonetDB](https://monetdb.org), is very fast and powerful, making such
analyses quite snappy even on such large data using normal desktops and laptops. Here's the
timing of the above query, which processes over 20 million records, on an ordinary laptop:
